Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-08-01 paper/paper.tex
Start resizing things

\begin{figure*}[p]
    \includegraphics*{gen-graph-cumulative-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33v.pdf}

@@

    \includegraphics*{gen-graph-cumulative-33ved.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-plain-connected.pdf}

@@

    \includegraphics*{gen-graph-cumulative-33ve-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-sip.pdf}

    \caption{Cumulative performance. The parallel versions, dotted, are always better in aggregate
    than the sequential versions, solid.}

\end{figure*}

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}

    \includegraphics*{gen-graph-histogram-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-plain-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups for unlabelled, undirected graphs. The histograms show the
    distribution of speedups for instances whose sequential runtime is at least $50$ milliseconds
    and no more than $100$ seconds (and so they under-represent superlinear speedups slightly).}
\end{figure*}

\begin{figure*}[t]
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}

    \includegraphics*{gen-graph-histogram-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-33v-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups for vertex-labelled graphs.}
\end{figure*}

\begin{figure*}[t]
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}

    \includegraphics*{gen-graph-histogram-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-33ved-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups for vertex-and edge-labelled, directed graphs.}
\end{figure*}

\begin{figure*}[t]
    \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}

    \includegraphics*{gen-graph-histogram-sip-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-histogram-sip-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups for vertex-and edge-labelled, directed graphs.}
\end{figure*}

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, clique algorithm.}
\end{figure*}

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t2.pdf}

@@

    \caption{Scalability and reproducibility, clique algorithm, Cilk.}
\end{figure*}

\begin{figure*}[p]
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, McSplit algorithm.}
\end{figure*}

>>>>

\begin{figure*}[tb]
    \includegraphics*{gen-graph-cumulative-plain.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33v.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33ved.pdf}

@@

    \includegraphics*{gen-graph-cumulative-plain-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-33ve-connected.pdf}
    \hfill
    \includegraphics*{gen-graph-cumulative-sip.pdf}

    \caption{Cumulative performance. The parallel versions, dotted, are always better in aggregate
    than the sequential versions, solid.}
\end{figure*}

\begin{figure*}[tb]
    \includegraphics*{gen-graph-scatter-plain-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33v-mcsplit-vs-mcsplit-par-t32.pdf}

@@

    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-mcsplit-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-kdown-vs-kdown-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-sip-mcsplit-vs-mcsplit-par-t32.pdf}

    \caption{Per-instance speedups. The $x$-axis is sequential performance and the $y$-axis is 32
    threaded performance, so points below the diagonal line represent a speedup.}
\end{figure*}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-33ved-clique-par-t32r-vs-clique-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, clique algorithm.}
\end{figure}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-33ved-clique-cilk-t32r-vs-clique-cilk-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-33ved-clique-vs-clique-cilk-t2.pdf}

@@

    \caption{Scalability and reproducibility, clique algorithm, Cilk.}
\end{figure}

\begin{figure}[tb]
    \includegraphics*{gen-graph-scatter-plain-mcsplit-par-t32r-vs-mcsplit-par-t32.pdf}
    \hfill
    \includegraphics*{gen-graph-scatter-plain-mcsplit-vs-mcsplit-par-t2.pdf}

@@

    \caption{Scalability and reproducibility, McSplit algorithm.}
\end{figure}
